---
title: "Charles C. Lanfear <br> Curriculum vitae"
#date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    #CDS
    css: ["https://use.fontawesome.com/releases/v5.7.2/css/all.css", "style/one-column.css"]
    #offline
    #css: [one-column.css, "fontawesome-free-5.8.1-web/css/all.css"]
    number_sections: false
    toc: false
    toc_float: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(stringr)
library(knitr)

publications <- readxl::read_xlsx("./cv_data/publications.xlsx")

cv_entries <- readxl::read_xlsx("./cv_data/cv_entries.xlsx")

```

<div class="grid-container">
<!-- top row -->
```{r summary, child = 'content/summary.Rmd'}
```

```{r contact-info, child = 'content/contact-info.Rmd'}
```
</div>

## Education {.education .nohead}
```{r, eval= TRUE}
cv_entries %>% 
  arrange(desc(year_begin)) %>%
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  # mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year_begin, what) %>% 
  kable()
```

## Research {.tabset .output-header}
### Publications {.nohead .publications}
```{r}
publications_table <- publications %>%
  arrange(desc(year), authors) %>%
  mutate(author_year = str_c(authors, ". ", year, ". ")) %>%
  mutate(title = ifelse(!is.na(url), str_c("[", title, "](", url, ")"), title)) %>% #turn title into link
  mutate(citation = ifelse(type == "article",
                           str_c(author_year, str_c(title, "."), str_c("*",venue,"*"), issue, sep = " "),
                           str_c(author_year, str_c(title, "."), str_c("*",venue,"*"), sep = " "))) %>%
  mutate(citation = str_replace(citation, "CC Lanfear", "**CC Lanfear**"))

publications_table %>%
  filter(type == "article") %>% 
  select(citation) %>%
  knitr::kable()

```

### Reports {.nohead .reports}

```{r}
publications_table %>%
  filter(type == "report") %>% 
  select(citation) %>%
  knitr::kable()
```

### Talks {.nohead .talks}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'talk') %>% 
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  arrange(desc(date)) %>%
  mutate(date = format(date, format = "%b %e, %Y")) %>%
  select(date, what) %>% 
  kable()
```

### Posters {.nohead .posters}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  arrange(desc(date)) %>%
  mutate(date = format(date, format = "%b %e, %Y")) %>%
  select(date, what) %>% 
  kable()
```

## Teaching {.tabset .output-header}
### Courses (Instructor) {.nohead .courses}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(url), str_c("[", what, "](", url, ")"), what)) %>%
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

### Workshops {.nohead .workshops}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'workshop') %>% 
  arrange(desc(date)) %>%
  mutate(what = ifelse(!is.na(url), str_c("[", what, "](", url, ")"), what)) %>%
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  mutate(date = format(date, format = "%b %e, %Y")) %>%
  select(date, what) %>% 
  kable()
```

### Lectures {.nohead .lectures}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'lecture') %>% 
  mutate(what = ifelse(!is.na(url), str_c("[", what, "](", url, ")"), what)) %>%
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  mutate(date = format(date, format = "%b %e, %Y")) %>%
  select(date, what) %>% 
  kable()
```

### Courses (TA) {.nohead .courses}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'teaching_ta') %>% 
  arrange(desc(year_end)) %>%
  mutate(what = ifelse(!is.na(url), str_c("[", what, "](", url, ")"), what)) %>%
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

## Other {.tabset .output-header}
### Grants and awards {.nohead .grants}
```{r, eval= TRUE}
cv_entries %>% 
  arrange(desc(year_begin)) %>%
  filter(type == 'grants_and_awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>%
  select(year, what) %>% 
  kable()
```

### Media coverage {.nohead .media}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'media') %>%
  arrange(desc(date)) %>%
  mutate(what = ifelse(!is.na(url), str_c("[", what, ".](", url, ")"), what)) %>% #turn title into link
  mutate(date = format(date, format = "%b %e, %Y")) %>%
  mutate(citation = str_c(what, " *", where, "*")) %>%
  select(date, citation) %>% 
  kable()
```

### Service {.nohead .service}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = str_c(what, ", ", where)) %>%
  mutate(year = case_when( 
           !is.na(year_end) & !is.na(year_begin) ~ str_c(year_begin, " --- ", year_end),
           is.na(year_end) & !is.na(year_begin) ~ year_begin,
           !is.na(year_end) & is.na(year_begin) ~ year_end,
           TRUE ~ "ERROR"
           )) %>% 
  mutate(year_begin = ifelse(is.na(year_begin), year_end, year_begin)) %>%
  arrange(desc(year_begin)) %>%
  select(year, what) %>% 
  kable()
```

### Reviews {.nohead .service}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'reviewer') %>%
  select(what) %>% 
  kable()
```

### Selected work experience {.nohead .work}
```{r, eval= TRUE}
cv_entries %>% 
  filter(type == 'work') %>% 
  arrange(desc(str_sub(year_end, -4, -1))) %>%
  mutate(what = ifelse(!is.na(additional_info), 
    str_c(what, "<br>", where, "<br>", additional_info),
    str_c(what, "<br>", where))) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

